|

### 2023-04-02 paper_comparison/paper_comparison/paper_comparison.Rmd
don't need the x_dist part in appendix
add multiple citations for F power affected by x dist

(fix the tense issue - rank: low)

(fix the notation issue (bold?) - rank: low)

@@

More typically, residuals will be plotted, as a scatter plot against the predicted values and each of the explanatory variables to scrutinize their relationships. If there are any visually discoverable patterns, the model is potentially misspecified. In general, one looks for noticeable departures from the model like non-linear dependency or heteroskedasticity. However, correctly judging a residual plot where no pattern exists can be a painstakingly difficult task for humans. It is especially common, particularly among students, to misinterpret patterns that are "random noise" and "random deviation from a model" [@loy2021bringing]. It is also possible to conduct hypothesis tests for non-linear dependence [@ramsey_tests_1969], and use a Breusch-Pagan test [@breusch_simple_1979] for heteroskedasticity.

@@

Although it is unusual to consider fitted value distribution or predictor distribution in power analysis, it is not so surprised that the power of conventional tests vary because of fitted value distribution. For instance, the power of the RESET test which is effectively a F test depends on the realizations of the additional predictors included in the auxiliary regression equation [@jamshidian2007study]. And those additional predictors are linear transformation of random vectors following certain predictor distributions. What is truly unexpected is the huge variability in power of conventional tests compared to visual tests. The discrete uniform distribution constantly produce the highest power while the normal distribution and the lognormal distribution produce the lowest power for non-linearity and heteroskedasticity pattern respectively. The difference in power corresponding to different distributions peak at around 90% when the effect size is at a moderate level. This huge difference is undesirable as is not uncommon for analysts to omit the factor of predictor distribution in power calculation and sample size calculation.

>>>>

@@

More typically, residuals will be plotted, as a scatter plot against the predicted values and each of the explanatory variables to scrutinize their relationships. If there are any visually discoverable patterns, the model is potentially misspecified. In general, one looks for noticeable departures from the model like non-linear dependency or heteroskedasticity. However, correctly judging a residual plot where no pattern exists can be a painstakingly difficult task for humans. It is especially common, particularly among students, to misinterpret patterns that are random noise and random deviation from a model [@loy2021bringing]. It is also possible to conduct hypothesis tests for non-linear dependence [@ramsey_tests_1969], and use a Breusch-Pagan test [@breusch_simple_1979] for heteroskedasticity.

@@

Although it is unusual to consider fitted value distribution or predictor distribution in power analysis, it is not so surprised that the power of conventional tests vary because of fitted value distribution. For instance, the power of the RESET test which is effectively a F test depends on the realizations of the additional predictors included in the auxiliary regression equation [@jamshidian2007study; @olvera2019relationship; @zhang2018practical]. And those additional predictors are linear transformation of random vectors following certain predictor distributions. What is truly unexpected is the huge variability in power of conventional tests compared to visual tests. The discrete uniform distribution constantly produce the highest power while the normal distribution and the lognormal distribution produce the lowest power for non-linearity and heteroskedasticity pattern respectively. The difference in power corresponding to different distributions peak at around 90% when the effect size is at a moderate level. This huge difference is undesirable as is not uncommon for analysts to omit the factor of predictor distribution in power calculation and sample size calculation.
